### 2016-06-26 sec4_baseline.tex
A complete version

\begin{figure*} [t]
\center
\includegraphics[width=\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

@@

\eat{
Before moving on to find the value of $\eta$, 
we first use $\rho_{G,L,K}(T)$ to define the \emph{min-spanned valid subsequence} 
of a sequence $T$. In simple words, $\rho_{G,L,K}(T)$ is the 
subsequence of $T$ with the smallest range and is valid wrt. $K,L,G$. 
%Let $\eta_T$ denote
%the range of $\rho_{G,L,K}(T)$.
To guarantee that no valid patterns are missing, $\eta$ needs
to be greater than the range of $\rho_{G,L,K}(T)$ for any
valid sequence $T$. To see this, consider an arbitrary valid sequence $T$.
Since each partition contains $\eta$ snapshots,
if $\eta \geq \range(\rho_{G,L,K}(T))$ holds, $\rho_{G,L,K}(T)$ must be completely located in one partition. Therefore, the patterns associated with $T$ would not be missing.
Formally, $\eta$ can be computed as:
\begin{equation}
\eta = \max\{\range(\rho_{G,L,K}(T)) | T \text{ is valid wrt. } G,L,K\}
\end{equation}

Directly compute such $\eta$ is challenging. However,
we provide the following theorem which states a bounded estimation on $\eta$: 
}

@@

\eat{
Note that Theorem~\ref{THM:RP_ETA} does not state the optimal value of $\eta$
for a given $G,L,K$. However, for any $G,L,K$, $\eta$ does not differ from
the optimal value by at most $L-1$. To see this, for any $G,L,K$, we can
generate a sequence $T$ by repeating the following pattern, a $L$-segment followed by $G$-gap. 
The repetition stops when $|T|\geq K$. Apparently $T$ is valid wrt. $G,L,K$.
It is easy to see that $T$ is minimal valid subsequence of itself, then $\eta^*  \geq \range(T) \geq (\lceil \frac{K}{L}\rceil -1)(G-1) + K$.
Therefore $\eta-\eta^* \leq L-1$.
}

\begin{algorithm}[h]
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

@@

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process. It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}). 
%The join of candidate $c$ and cluster $s$ creates a
%new candidate $c'$ (Line~\ref{code:ls-join}).  
After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.

%ADD EXPLANATIONS TO THE SECOND AND THIRD PRUNING RULES.

%After join, there are two prunings. First, 
%all new candidates with objects set less than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second,
%existing candidates with max time sequences no greater 
%than $j-G$ are pruned (Line~\ref{code:ls-m-prun}). 
% 
%
%During the sweeping, candidates in $\mathbf{C}$ join with $S_j$.
%
% Initially, all the clusters 
%
%During scanning, a set of pattern candidates is maintained.
%When all snapshots are scanned, the remaining candidates are the true patterns.
%The detail of LSM is presented in Algorithm~\ref{algo:line-sweep}.
%A candidate set $C$ is maintained throughout the algorithm(line~\ref{code:ls-can-set}). $C$
%is initialized by inserting clusters at $S_t$ (lines~\ref{code:ls-init-start}-\ref{code:ls-init-end}).
%During scanning snapshot $S_j$, candidates in $C$ are joined with clusters at $S_j$. In
%the join, a candidate grows its temporal sequence while potentially reduces its object set. After the join,
%false patterns are deleted (line~\ref{code:ls-remove}). 
%Note that the size of $C$ is always decreasing, therefore the complexity of LSM $\lambda_t$ is $O(\eta|S_t||\overline{S}|)$,where $|\overline{S}|$ is the average snapshot size in $\lambda_t$.

@@

\begin{algorithm}[h]
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$ pair} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep algorithm for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

\begin{figure*} [t]
\center
\includegraphics[width=0.9\textwidth]{trm.eps}
\caption{Work flow of Temporal Replication and Parallel Mining (TRPM). (a)(b) correspond to the first map-reduce cycle which clusters objects in each snapshot;  (c)(d) correspond to the second map-reduce cycle, which uses TRPM to detect GCMP in parallel.}
\label{fig:trm}
\end{figure*}

@@

@@

\begin{algorithm}[h]
\small
\caption{Line Sweep Mining}
\label{algo:line-sweep}
\begin{algorithmic}[1]
\Require $\lambda_t = \{S_t, ..., S_{t+\eta-1}\}$
\State{$C \gets \{\}$} \Comment{Candidate set} \label{code:ls-can-set}
\ForAll{clusters $s$ in snapshot $S_t$} 
\label{code:ls-init-start}
\If{$|s| \geq M$}
\State $C\leftarrow C\cup \{\langle s, t \rangle \}$
\EndIf
\EndFor
\label{code:ls-init-end}
\ForAll{$S_j \in \{S_{t+1},\ldots,S_{t+\eta-1}\}$} \label{code:ls-sweep-starts}
	\State $N \gets \{\}$
	\ForAll {$(c,s) \in C \times S_j$} \label{code:ls-join-start}
		\State {$c' \gets \langle c.O \cap s.O, c.T \cup \{j\} \rangle$} \label{code:ls-join}
		\If {$c'.T$ is valid} 
			\State output $c'$
		\ElsIf{$|c'.O| \geq M$}
			\State $N\leftarrow N\cup \{c'\}$ \label{code:ls-m-prun}	
		\EndIf
	\EndFor \label{code:ls-join-ends}
	\ForAll {$c \in C$}
		\If{$j-\max(c.T)\geq G$}\label{code:ls-g-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
			\State output $c$, if $c$ is a valid pattern
		\EndIf  \label{code:ls-g-prune-ends}
		\If{$c$'s first segment is less than $L$}\label{code:ls-l-prune-starts}
			\State $C\leftarrow C-\{c\}$ 
		\EndIf\label{code:ls-l-prune-ends}
	\EndFor
	\State $C\leftarrow C\cup N$
\EndFor\label{code:ls-sweep-ends}
\State output valid patterns in  $C$  \label{code:ls-valid-check}
\end{algorithmic}
\end{algorithm}

@@

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process. It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}).

After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.

@@

\begin{algorithm}[h]
\small
\caption{Temporal Replication and Parallel Mining}
\label{algo:trm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State $\eta \gets (\lceil \frac{K}{L} \rceil -1)*(G-1)+K+L-1$
\State {---Map Phase---}
\label{code:trm-map-start}
\ForAll{snapshots $S_t$}
	\ForAll{$i \in 1...{\eta-1}$}
		\State emit key-value pair $\langle \max(t-i,0), S_t \rangle$ 
	\EndFor  
\EndFor
\label{code:trm-map-end}
\State {---Partition and Shuffle Phase---}
\label{code:trm-par-start}
\ForAll{key-value pairs $\langle t, S \rangle$ pair} 
\State group-by $t$ and emit a key-value pair $\langle t, \lambda_t\rangle$, where $\lambda_t = \{S_t, S_{t+1}, .. S_{t+\eta-1}\} $
\EndFor
\label{code:trm-par-end}
\State {---Reduce Phase---}
\label{code:trm-red-start}
\ForAll{key-value pairs $\langle t,\lambda_t \rangle$}
\State call line sweep algorithm for partition $\lambda_t$
\label{code:trm-red-end}
\EndFor
\end{algorithmic}
\end{algorithm}

### 2016-06-26 sec5_spm.tex
A complete version

%An important concern in design parallel algorithms is the distribution of work loads.  
%Traditionally, the quality of a partition strategy 
%is measured based on two aspects: (1) the number of result partition, which
%affects the maximum parallelism
%(2) the size balance of partitions, which affects the finishing
%time of a job. Unlike TRM where each partition
%contains equal-sized snapshots, the size distribution 
%of stars in SPM remains unknown.
%Nevertheless, we notice that, in SPM, the total sizes of 
%stars are invariant. Therefore, the quality of a star partition
%can be formalized as the \emph{skewness}, which is the maximum star size
%among all stars. Smaller \emph{skewness} naturally results in more partitions
%and less imbalance.
%}

@@

%To determine the optimal vertex orders with the objective of minimizing $\Gamma$, 
%we can use a linear algebra model as follows:  
%Let $G_A$ be an aggregate graph, with a $n \times n$ adjacent matrix $J$.
%A vertex order is in fact a permutation of $J$. Therefore,
%the adjacent matrices of any reordered graphs can be represented as $PJP^T$
%where $P \in \mathbb{P}$ is a 
%\emph{permutation matrix}~\footnote{an identity matrix with rows shuffled} with dimension $n$.
%Since in star partition, we assign each edge $e(i,j)$ in $G_A$ to the lower vertex, 
%then the matrix $B=\triu(PJP^T)$~\footnote{\text{triu} is the upper triangle part of a matrix}
%represents the assignment matrix wrt. $P$ (i.e., $b_{i,j} = 1$ if vertex $j$ is in star $Sr_i$).
%Let vector $\vec{b}$ be the \textit{one}\footnote{every element in $\vec{b}$ is $1$} 
%vector of size $n$. Let $\vec{c} = B\vec{b}$, then each $c_i$ 
%denotes the number of edges in star $Sr_i$. Thus, $\Gamma$ can be represented
%as the infinity norm of $B\vec{b}$. Let $\Gamma^*$ be the minimum $\Gamma$ among all vertex orders. 
%$\Gamma^*$ can then be formulated as follows:
%\begin{equation}
%\Gamma^* = \min_{P \in \mathbb{P}}{||B\vec{b}||_\infty} \text{ ,where } ||B\vec{b}||_\infty = \max_{1\leq j \leq n}(c_j)
%\end{equation}

@@

%
%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
%When $\eta$ is small, TRM perform good parallelism. However, wh
%
%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
%%which surrenders the benefit of parallelism.
%\eat{
%Although TRPM works in a parallel way, we observe two inefficiencies. First, the
%performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
%When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
%the parallel execution of line sweep algorithm may discover the same pattern from
%multiple partitions, which introduces redundant work. To resolve the two limitations,
%we design a novel \emph{Star Partition and Mining} algorithm.
%}
%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.

@@

\begin{definition}[Maximal $G$-connected Subsequence]
A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, i.e., $\exists i\leq j, T' = T(i,\ldots,j)$ , (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
\end{definition}
%Hence, our idea is to examine the validity of object pairs. If $(o_i,o_j)$ itself is not a valid GCMP pattern, then all the supersets containing $(o_i,o_j)$ can be pruned. For instance, $(XXX,XXX)$ are not connected in Figure~\ref{} and all its supersets can be pruned.

@@

%Not that, although $T_1$ is not a candidate sequence, it can be simplified
%to a candidate sequence (i.e, $T_2$). Generally, for any time sequence $T$, 
%if it does not contain a \emph{candidate sequence}, then it cannot contribute
%to any valid patterns. In fact, only the candidate sequence inside $T$ affects
%the final patterns. Therefore, we may use the candidate sequence to simplify edges in 
%a star. During the simplification, if an edge results in a candidate
%sequence of size zero, then it is removed from the star. Otherwise,
%the simplified edge is kept. By so doing, the size of the new star
%is much smaller.

@@

\eat{
Nevertheless, if there exists a $T^\#$ of $T$, then $T^\#$ is unique
as stated in the following theorem:
\begin{theorem}
For any sequence $T$, if $T$'s simplified sequence is not empty, then
there exists a unique $T^\#$ wrt $T$.
\end{theorem}
\begin{proof}
We prove by contradiction. Suppose there are two simplified sequences $T_A^\#$ and $T_B^\#$ of the same $T$. We prove that, unless $T_B^\# \equiv T_A^\#$, $T_A^\#$ can always be enlarged, which leads to a contradiction. For simplicity, we use $\overline{ab}$ to denote the segment of a sequence from timestamp $a$ to timestamp $b$.
Consider the timestamps $T_C=T_B^\# - T_A^\#$. If $T_C = \emptyset$, then $T_A^\# \equiv T_B^\#$ naturally.

Next, since $T_C \not \equiv \emptyset$, W.L.O.G, let the first timestamp in $T_A^\#$ be greater than the first timestamp $T_B^\#$. Consider the general setting: $\overline{ab}$ is the first candidate sequence in $T_A^\#$;  $\overline{ef}$
is a consecutive sequence in $T_C$ and $f < a$; $\overline{cd}$ is the next candidate sequence of $\overline{ef}$ in $T_B^\#$; $\overline{gh}$ is the previous candidate sequence of $\overline{ef}$ in $T_B^\#$; Categorize on the gaps between $\overline{ef}$ and  $\overline{cd}$, $\overline{gh}$,
there are four cases to be considered. 
We demonstrate the cases in Figure~\ref{fig:proof_thm_3}:
\begin{figure}[h]
\centering
\includegraphics[width=0.46\textwidth]{thm3proof.eps}
\caption{Proof of theorem 3 with the four cases.}
\label{fig:proof_thm_3}
\end{figure}
\begin{itemize}
\item Case (a): $c-f = 1$, that is $\overline{ef}$ is part of a longer consecutive segment $\overline{ed}$. Since timestamp $c$ is in $T_A^\#$, $T_A^\#$ can be safely enlarged by increasing $\overline{ab}$ to $\overline{eb}$.
\item Case (b): $G \geq c-f> 1$. In this case, since $c\geq a$, then $a-f \leq G$. Further, since $\overline{ed}$ is not 
consecutive, $\overline{ef}$ must belongs to a larger consecutive segment $\overline{gf}$ with size no less than $L$. Therefore, adding $\overline{gf}$ to $\overline{ab}$ makes $\overline{gb}$ still a candidate sequence.
\item Case (c): $c-f > G$ and $e-h \leq G$. In this case, $\overline{ef}$ belongs to a candidate sequence $\overline{gf}$ in $T_B^\#$.  Since $\overline{gf}$ has no intersection with $\overline{ab}$, then adding $\overline{gf}$ to $T_A^\#$ is valid.
\item Case (d): $c-f > G$ and $ e- h > G$. In this case,  $\overline{ef}$ has to be a candidate sequence. Since $\overline{ef}$ has no intersection with $\overline{ab}$, adding $\overline{ef}$ to $\overline{ab}$ is valid.
\end{itemize}
In all cases, $T_A^\#$ can be enlarged, which contradicts with the assumption $T_A^\#$ is the simplified sequence. This completes the proof.
\end{proof}
}

\eat{
Next, we design an efficient simplification process with linear complexity.
It takes two rounds scan of $T$ as shown in Algorithm~\ref{algo:simp_prune}. 
In the first round, the consecutive portions of $T$ with size less than $L$ are removed.
In the second round, the maximal $G$-connected sequences of size less than $K$ are removed.

\begin{algorithm}
\caption{Edge Simplification}
\label{algo:simp_prune}
\begin{algorithmic}[1]
\Require $T$
\State{---$L$ Phase---}
\State $c \gets 0$
\For {$i \in (0,...,|T|)$}
	\If{$T[i] - T[i-1] > 1$} 
		\If{$i - c < L$} 
			\State $T$ remove $[c:i)$
		\EndIf
		\State $c \gets i$
	\EndIf
\EndFor
\State{---$G$-$K$ Phase---}
\State $s\gets 1$, $c\gets 0$
\For{$i \in (0: |T|)$}
	\If{$T[i] - T[i-1] > G$}
		\If{$s < K$}   
			\State $T$ remove $[c:i)$
		\EndIf
		\State {$c \gets i$, $s \gets 1$}
	\Else
		\State $s++$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}
}

@@

%IN THE PROOF, YOU NEED TO SHOW 1) $P$ IS NOT VALID 2) ALL THE SUPERSETS OF $P.O$ ARE NOT VALID.

@@

\begin{algorithm}[h]
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
%\ElsIf{$c$ is a valid pattern}
%\State{output $c$}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
%	
%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
%					\State {$C'\leftarrow C'\cup \{c'\}$}
%					\ElsIf{$c'$ is a valid pattern}
%						\State{output $c'$}
%				\EndIf
%		\EndFor	\label{code:join-ends}
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Partition and Shuffle phase---}
\label{code:spm-shuffle-start}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
	%\State group-by $o_2$, emit $\langle o_2, Sr_{o_2} \rangle$
\EndFor
\label{code:spm-shuffle-end}

>>>>

@@

@@

@@

\begin{definition}[Maximal $G$-connected Subsequence]
A sequence $T'$ is said to be a maximal $G$-connected subsequence of $T$ if (1) $T'$ is the subsequence of $T$, i.e., $\exists i\leq j, T' = T(i,\ldots,j)$ , (2) $T'$ is $G$-connected, and (3) there exists no other subsequence $T''$ of $T$ such that $T'$ is the subsequence of $T''$ and $T''$ is G-connected.
\end{definition}

@@

@@

@@

@@

\begin{algorithm}[h]
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
\small
\caption{Star Partition and ApRiori Enumerator}
\label{algo:spm_overview}
\begin{algorithmic}[1]
\Require list of $\langle t, S_t \rangle$ pairs
\State {---Map phase---}
\label{code:spm-map-start}
\ForAll{$C \in S_t$}
	\ForAll {$o_1 \in C,  o_2 \in C, o_1 < o_2$}
	\State emit a $\langle o_1, o_2, \{t\}\rangle$ triplet~\label{code:spm-edge-direct}
	\EndFor
\EndFor
\label{code:spm-map-end}

\State {---Partition and Shuffle phase---}
\label{code:spm-shuffle-start}
\ForAll{$\langle o_1, o_2, \{t\}\rangle$ triplets} 
	\State group-by $o_1$, emit $\langle o_1, Sr_{o_1} \rangle$ 
\EndFor
\label{code:spm-shuffle-end}
